\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}

% suppress hyphenation
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

% format
\geometry{margin=0.4in}
\pagenumbering{gobble}

\begin{document}

% title
\begin{center}
    {\LARGE \textbf{Lillian Skyler Danforth}} \\
    \vspace{0.2cm}
    \small
    San Francisco, CA | \href{tel:+15404802622}{(540) 480-2622} | \href{mailto:danforthlily@gmail.com}{danforthlily@gmail.com} | \href{https://github.com/lilijoyskyseeker}{GitHub:lilijoyskyseeker} \\
    \vspace{-0.4cm}
\end{center}
    
\section*{\hspace*{1em} Education}
\vspace{-0.2cm}
\hrule
\vspace{0.3cm}
\textbf{\hspace*{1em}Cyber Security \& Network Administration}
\hfill January 2023 — May 2025 \\
\textit{Virginia Western Community College, Roanoke VA} \\
Relevant Studies: Cisco Networking, Linux Server Administration, Windows Server Administration, Database Management, Cloud Computing AWS, Cyber Security, Python, Java, Computer Troubleshooting and Repair, Agile, Scrum \\
\vspace{-0.3cm} \\
\textbf{\hspace*{1em}Electrical Engineering}
\hfill September 2021 — May 2022 \\
\textit{Rose-Hulman Institute of Technology, Terre Haute IN} \\
Relevant Studies: DC Circuits, Python, Java, Arduino, Calculus, Physics, Engineering Team Robotics \\
\vspace{-0.3cm} \\
\textbf{\hspace*{1em}Trade and Industrial Education: Electronics Technology}
\hfill August 2017 — May 2021 \\
\textit{Floyd S. Kay Technical Center, Lexington VA} \\
Relevant Studies: DC Circuits, AC Circuits, Digital Electronics, Robotics, Computer Programming, Computer Repair, Soldering, Electronic Prototyping\\

\vspace{-0.8cm}
\section*{\hspace*{1em} Experience}
\vspace{-0.27cm}
\hrule
\vspace{0.3cm}
\textbf{\hspace*{1em}Technical Book Editor} 
\hfill March 2024 — May 2024 \\
Technical edit of the "Introduction to Python and Spice for Electrical and Computer Engineers" textbook authored by \href{https://www.jimsquire.com/}{Jim Squire}. \\

\vspace{-0.8cm}
\section*{\hspace*{1em} Skills}
\vspace{-0.2cm}
\hrule
\vspace{0.3cm}
\begin{itemize}
    \item \textbf{Linux:} 6+ years experience with desktop, laptop, and server environments. \\
    Proficient with main Distro families: Debian, Arch, Red Hat, NixOS and Gentoo. \\
    Additional experience with derived distros like Ubuntu Server, Fedora, PopOS!, EndeavourOS and Nobara. \\ 
    Experience with managing remote and local installations including automatic updates, fully automated installations with nixos-anywhere, and fully declarative whole system configuration. \\
    Experience running various self hosted services including: Jellyfin, TheLounge IRC Client, NextCloud, Minecraft, FreshRSS, Copyparty, SAMBA, hosted with Caddy to act as the reverse proxy and to provide HTTPS. \\
    Experience with many server based tooling such as: Docker, Podman, Git, ZFS, Sanoid/Syncoid, Restic, QEMU, KVM, SOPS, Caddy, WireGuard, EXT4, UEFI, SSH, SSHFS, PAM, SQL, and Vim. \\
    \vspace{-0.7cm}
    \item \textbf{Other Operating Systems:} Experience with Windows 10/11, Windows Server, WinGet, Hyper-V, MacOS Tiger through Sequoia, various Apple services, IOS, and Android. \\
    \vspace{-0.7cm}
    \item \textbf{Programming:} Experience with Bash scripting for Linux automation, Basic knowledge of Python, Basic knowledge of Java, Extensive experience NixOS configuration and packaging for Nix, Experience with Arduino in hobbyist robotics competitions. \\
    \vspace{-0.7cm}
    \item \textbf{Hardware:} Extensive experience soldering, Experience with repairing and building desktops, laptops and servers, Experience with basic A/V equipment, Experience with basic networking equipment. \\
\end{itemize} 

\vspace{-1.1cm}
\section*{\hspace*{1em} Standout Projects}
\vspace{-0.2cm}
\hrule
\vspace{0.3cm}
\begin{itemize}
    \item Configured two-factor authentication for SSH key access using FIDO2, leveraging the motherboard TPM and/or a YubiKey as hardware authenticators. Thus allowing hardware locked SSH keys. \\
    \vspace{-0.5cm}
    \item Setup a fully automated backup solution involving: A 48 TB HDD array with ZFS as the filesystem, Sanoid/Syncoid for ZFS snapshots and backups to a second pool, and Restic for offsite backups to Backblaze B2 using mounted ZFS snapshots to allow fully atomic incremental backups. \\
    \vspace{-0.5cm}
    \item Fully automated remote installation and declarative NixOS configuration using nixos-anywhere and disko. Allowing 98\% automated setup/reinstallation of the server environment with the only manual step being authentication for secret access. \\
    \vspace{-0.5cm}
    \item Declarative sops based secret management shared across multiple machines and stored securely on a public GitHub repo without leaking secrets. \\
    \vspace{-0.5cm}
\end{itemize}
\end{document}